Naturalness in U(1) extensions of the MSSM

### 2015-01-20 paper/e6ssm-tuning-paper.tex
fixed small typos.

To further illustrate this point we looked at how the tuning compares for
low tuning benchmarks in the MSSM and E6SSM when the highscale
boundary condition, $M_X$ is raised.  The results of this are shown in
Fig.~\ref{Fig:BMs-varyMX}.

In the top left panel one can see that the MSSM tuning (green)
steadily climbs as the cutoff scale is increased, as one would expect
when the tuning originates from large soft masses entering from the
RGEs. The panel on the top right confirms this, showing that the
largest tuning contributions come from $\Delta_{A_t}$ and
$\Delta_{m_{H_u}^2}$ with the former being the larger sensitivity
until $M_X\approx 10^8$ GeV at which point $\Delta_{m_{H_u}^2}$ takes
over, leading to the small kink in overall tuning which can be seen in
the green curve in the top left panel. In thus case we have chosen a
point with large mixing which reduce the MSSM tuning somewhat.  this
does not eliminate the tuning as one there is still a string
sensitivity to $A_t$, but we did find that increasing $A_t$ lead less
fine tuning overall.

The E$_6$SSM tunings are rather more complicated.  By comparing them
to the MSSM tuning one can see that the scale at which the parameters
are defined is very important for determining which point is more fine
tuned.  In the bottom left panel one can see that the dependence of
the E$_6$SSM tuning on the cutoff is rather complicated, illustrating
that any statement about which model is more tuned depends on the
cutoff scale considered.

@@

By contrast the tuning for E$_6$SSM BM2 is very different.  This point
was chosen as it had much lighter stops and a gluino mass that is just
above the experimental limit of $1.4$ TeV \cite{}.  At $20$ TeV it was
not amongst the lowest tuned points, since at that scale the tree
level tuning from $M_{Z^\prime}$ dominates.  The reduction in $M_3$
means that $\Delta_{M_3}$ is substantially lower and only becomes the
dominant tuning very close to the GUT scale, giving a tuning at
$10^{16}$ GeV of $\approx 900$, which is below that of the other two
benchmark points.  Since large mixing was also used to reduce allow
lighter stops, we see initially a large contribution from
$\Delta_{A_t}$ as we did in the MSSM benchmark.  [Last thing that needs to be explained - why do $\Delta_{M_3}$ and $\Delta_{m_{H_u}^2}$ start to decrease at $M_X$.  I'm guessing something funny to do with their values and also  $m_{Q}^2$ and $M_3$ at the highscales.  but i need to see the numbers to know.]

>>>>

To further illustrate this point we looked at how the tuning compares
for low tuning benchmarks in the MSSM and E6SSM when the highscale
boundary condition, $M_X$ is raised. The results of this are shown in
Fig.~\ref{Fig:BMs-varyMX}. Since the behaviour is a quite complicated
we now discuss these in detail as it provides some insight into the
many differences in the tuning between the two models.

In the top left panel one can see that the MSSM tuning (green)
steadily climbs as the cutoff scale is increased, as one would expect
when the tuning originates from large soft masses entering from the
RGEs. The panel on the top right confirms this, showing that the
largest tuning contributions come from $\Delta_{A_t}$ and
$\Delta_{m_{H_u}^2}$ with the former being the larger sensitivity
until $M_X\approx 10^8$ GeV at which point $\Delta_{m_{H_u}^2}$ takes
over, leading to the small kink in overall tuning which can be seen in
the green curve in the top left panel. In thus case we have chosen a
point with large mixing which is known to reduce the MSSM tuning.  We
found this does not eliminate the tuning as there is still a strong
sensitivity to $A_t$, but we did find that increasing $A_t$ lead less
fine tuning overall fo the points we looked at.

The E$_6$SSM tunings are rather more complicated as there are more
sources of fine tuning.  By comparing them to the MSSM tuning one can
see that the scale at which the parameters are defined is very
important for determining which point is more fine tuned.  In the
bottom left panel one can see that the dependence of the E$_6$SSM
tuning on the cutoff is rather complicated, illustrating that any
statement about which model is more tuned depends on the cutoff scale
considered.

@@

By contrast the tuning for E$_6$SSM BM2 is very different.  This point
was chosen as it had much lighter stops and a gluino mass that is just
above the experimental limit of $1.4$ TeV \cite{}.  At $20$ TeV it was
not amongst the lowest tuned points, since at that scale the tree
level tuning from $M_{Z^\prime}$ dominates.  The reduction in $M_3$
means that $\Delta_{M_3}$ is substantially lower and only becomes the
dominant tuning very close to the GUT scale, giving a tuning at
$10^{16}$ GeV of $\approx 900$, which is below that of the other two
benchmark points.  Since large mixing was also used to reduce allow
lighter stops, we see initially a large contribution from
$\Delta_{A_t}$ as we did in the MSSM benchmark.  [Last thing that needs to be explained - why do $\Delta_{M_3}$ and $\Delta_{m_{H_u}^2}$ start to decrease at large $M_X$.  I'm guessing something funny to do with their values and also  $m_{Q}^2$ and $M_3$ at the highscales.  but i need to see the numbers to know.]
